### 2024-07-31 paper/tex/02-overview.tex
edit and prepare for jfp
WIP: fix references, add appendix
prettify + minor edits

Generally, any term and type of \systemf can be embedded into \fexists in
multiple ways corresponding to different evaluation strategies of \systemf,
which we will cover in more detail in \cref{sec:rel-to-systemf}.

\Cref{fig:polarization-examples} illustrates how standard \systemf types are
polarized when call-by-value evaluation is presumed.

@@

Using the examples provided in \cref{fig:polarization-examples}, we now showcase 
the type inference capabilities and restrictions of \fexists

\begin{figure}[h]
  \begin{align*}
    [[double]] &: [[↓(Int → ↑Int)]] \\
    [[map]] &: [[↓(∀α⁺.∀β⁺.↓(α⁺ → ↑β⁺) → List α⁺ → ↑List β⁺)]] \\
    [[len]] &: [[↓(∀α⁺.List α⁺ → ↑Int)]] \\
    [[choose]] &: [[↓(∀α⁺.α⁺ → α⁺ → ↑α⁺)]] \\
    [[id]] &: [[↓(∀α⁺.α⁺ → ↑α⁺)]] \\
    [[auto]] &: [[↓(↓(∀α⁺.α⁺ → ↑α⁺) → (∀α⁺.α⁺ → ↑α⁺))]]
  \end{align*}
  \caption{Polarization of \systemf types}
  \label{fig:polarization-examples}
\end{figure}

@@

\paragraph*{Polymorphic Self-application.}
  Unlike predicative systems, \fexists permits self-application of polymorphic
  functions. For instance, $[[id]]$ can be applied to itself resulting in a
  suspended polymorphic computation of type $[[↓(∀α⁺.α⁺ → ↑α⁺)]]$, which, in
  turn, can be applied to itself:
  $$[[· ; Φ ⊢ let x = id(id); let y = x(x); return y : ↑↓(∀α⁺.α⁺ → ↑α⁺)]]$$

>>>>

Generally, any term and type of \systemf can be embedded into \fexists in
multiple ways corresponding to different evaluation strategies of \systemf,
which we will cover in more detail in \cref{sec:rel-to-systemf}.
\Cref{fig:polarization-examples} illustrates how standard \systemf types are
polarized when call-by-value evaluation is presumed.

@@

Using the examples provided in \cref{fig:polarization-examples}, we now showcase 
the type inference capabilities and restrictions of \fexists.

\begin{figure}[t]
  \begin{align*}
    [[double]] &: [[↓(Int → ↑Int)]] \\
    [[map]] &: [[↓(∀α⁺.∀β⁺.↓(α⁺ → ↑β⁺) → List α⁺ → ↑List β⁺)]] \\
    [[len]] &: [[↓(∀α⁺.List α⁺ → ↑Int)]] \\
    [[choose]] &: [[↓(∀α⁺.α⁺ → α⁺ → ↑α⁺)]] \\
    [[id]] &: [[↓(∀α⁺.α⁺ → ↑α⁺)]] \\
    [[auto]] &: [[↓(↓(∀α⁺.α⁺ → ↑α⁺) → (∀α⁺.α⁺ → ↑α⁺))]]
  \end{align*}
  \caption{Polarization of \systemf types}
  \label{fig:polarization-examples}
\end{figure}

@@

\paragraph*{Polymorphic Self-application}
  Unlike predicative systems, \fexists permits self-application of polymorphic
  functions. For instance, $[[id]]$ can be applied to itself resulting in a
  suspended polymorphic computation of type $[[↓(∀α⁺.α⁺ → ↑α⁺)]]$, which, in
  turn, can be applied to itself:
  $$[[· ; Φ ⊢ let x = id(id); let y = x(x); return y : ↑↓(∀α⁺.α⁺ → ↑α⁺)]]$$

### 2024-07-31 paper/tex/04-algorithm.tex
prettify + minor edits

\begin{figure}[t]

  \begin{minipage}[t]{0.49\textwidth}
      Negative Algorithmic Variables\\
      $[[α̂⁻]]$, $[[β̂⁻]]$, $[[γ̂⁻]]$, \dots\\
  \end{minipage}%
  \begin{minipage}[t]{0.49\textwidth}
      Positive Algorithmic Variables\\
      $[[α̂⁺]]$, $[[β̂⁺]]$, $[[γ̂⁺]]$, \dots\\
  \end{minipage}

@@

\paragraph*{Auxiliary Functions}
\begin{itemize}
  \item
    We define $[[dom(SC)]]$---the domain of constraint set $[[SC]]$---as a set of
    algorithmic variables that it restricts. Similarly, we define $[[dom(Θ)]]$---the
    domain of instantiation context $[[Θ]]$---as a set of algorithmic variables that
    $[[Θ]]$ associates with their contexts.  
  \item We write $[[Θ(α̂±)]]$ to denote the
    declarative context associated with $[[α̂±]]$ in $[[Θ]]$. 
  \item $[[uv(uN)]]$ and $[[uv(uP)]]$ denote the set of free algorithmic variables in $[[uN]]$ and
    $[[uP]]$ respectively.
  \item We write $[[Γ ⊢ Θ]]$ to denote that each
    declarative context associated with an algorithmic variable in $[[Θ]]$ is 
    a subcontext (subset) of $[[Γ]]$.
\end{itemize}

@@

    % Define nodes
    \node[] (1) {Negative Subtyping\\$[[Γ ; Θ ⊨ uN ≤ iM ⫤ SC]]$\\(\cref{fig:alg-subtyping})};
    \node[below of=1] (3) {Positive Subtyping\\$[[Γ ; Θ ⊨ uP ≥ iQ ⫤ SC]]$\\(\cref{fig:alg-subtyping})};
    \node[left=1.5cm of 3] (2) {Constraint Merge\\$[[Θ ⊢ SC1 & SC2 = SC3]]$\\(\cref{sec:constraint-merge})};
    \node[right=1.5cm of 3] (5) {Unification\\ $[[Γ ; Θ ⊨ uN ≈u iM ⫤ UC]]$\\ $[[Γ ; Θ ⊨ uP ≈u iQ ⫤ UC]]$\\(\cref{sec:unification})};
    \node[below of=3] (4) {Upgrade\\$[[upgrade Γ ⊢ iP to Δ = iQ]]$\\(\cref{sec:lub})};
    \node[below of=2] (6) {Least Upper Bound\\$[[Γ ⊨ iP1 ∨ iP2 = iQ]]$\\(\cref{sec:lub})};
    \node[below of=6] (7) {Anti-Unification\\$[[Γ ⊨ iP1 ≈au iP2 ⫤ ( Ξ , uQ , aus1 , aus2 )]]$\\$[[Γ ⊨ iN1 ≈au iN2 ⫤ ( Ξ , uM , aus1 , aus2 )]]$\\(\cref{sec:antiunification})};
    \node[below of=5] (8) {Unification Constraint Merge\\$[[Θ ⊢ UC1 & UC2 = UC3]]$\\(\cref{sec:constraint-merge})};

    % Define edges
    \draw[->] (1) to (2);
    \draw[->] (1) to (3);
    \draw[->] (1) to node[above, draw=none]{$\ottkw{nf}$} (5);
    \draw[->] (2) to (3);
    \draw[->] (2) to (6);
    \draw[->] (3) to (4);
    \draw[->] (3) to node[above, draw=none]{$\ottkw{nf}$} (5);
    \draw[->] (4) to (6);
    \draw[->] (5) to (8);
    \draw[->] (6) to node[left, draw=none]{$\ottkw{nf}$} (7);
  \end{tikzpicture}  
  \caption{Dependency graph of the subtyping algorithm}
  \label{fig:alg-subtyping-graph}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \begin{tikzpicture}
    [>={Stealth[scale=2]},node distance=2.2cm,every node/.style={draw,rectangle},every text node part/.style={align=center}]
    % Define nodes
    \node[] (1) {Positive Inference\\$[[Γ; Φ ⊨ v : iP]]$};
    \node[right=1.4cm of 1] (2) {Negative Inference\\$[[Γ; Φ ⊨ c : iN]]$};
    \node[right=1.2cm of 2] (3) {Application Inference\\$[[Γ ; Φ ; Θ1 ⊨ uN ● args ⇒> uM ⫤ Θ2 ; SC]]$};
    \node[below=0.6cm of 2] (7) {Minimal Instantiation\\$[[Γ ⊢ uP SC minby uσ]]$\\(\cref{sec:constraint-singularity})};
    \node[below=0.5cm of 7] (8) {Constraint Singularity\\$[[SC singular with uσ]]$\\(\cref{sec:constraint-singularity})};
    \node[right=0.3cm of 7] (4) {Constraint Merge\\$[[Θ ⊢ SC1 & SC2 = SC3]]$\\(\cref{sec:constraint-merge})};
    \node[left=0.3cm of 7] (6) {Negative Subtyping\\$[[Γ ; Θ ⊨ uN1 ≤ iN2 ⫤ SC]]$\\(\cref{sec:subtyping-algorithm})};
    \node[below=0.9cm of 6] (5) {Positive Subtyping\\$[[Γ ; Θ ⊨ uP1 ≥ iP2 ⫤ SC]]$\\(\cref{sec:subtyping-algorithm})};
    \draw[->] ([yshift=-.2cm]2.west) to ([yshift=-.2cm]1.east);
    \draw[->] ([yshift=+.2cm]1.east) to ([yshift=+.2cm]2.west);
    \draw[->, bend right=20] (3) to (1);
    \draw[->] (2) to (3);
    \draw[->] (2) to (4);
    \draw[->] (2) to (7);
    \draw[->] (3) to (4);
    \draw[->] (7) to (8);
    \draw[->] (1.south west) |- (5);
    \draw[->] (3) |- (5.south east);
    \draw[->] (2) to (6);
  \end{tikzpicture}  
  \caption{Dependency graph of the typing algorithm}
  \label{fig:alg-typing-graph}
\end{figure}

@@

\begin{figure}[t]
  \begin{minipage}{0.49\textwidth}
    `$[[SC singular with uσ]]$' means:
    \begin{itemize}[leftmargin=*]
      \item[$+$] for any \emph{positive} constraint entry $[[scE ∊ SC]]$ restricting 
        a variable $[[β̂⁺]]$, there exists $[[iP]]$ such that $[[scE singular with iP]]$
        (as defined in \cref{fig:constraint-entry-singularity}),
        and $[[ [uσ]β̂⁺ = iP ]]$; and
      \item[$-$] the symmetric property holds for all \emph{negative} $[[scE ∊ SC]]$; and
      \item[$\notin$] for any $[[α̂± ∉ dom(SC)]]$, $[[ [uσ]α̂± = α̂± ]]$.
    \end{itemize}
    \caption{Singular Constraint}
    \label{fig:constraint-singularity}
  \end{minipage}
  \begin{minipage}{0.48\textwidth}
    \ottdefnSINGLabeled
    \caption{Singular Constraint Entry}
    \label{fig:constraint-entry-singularity}
  \end{minipage}
\end{figure}

>>>>

\begin{figure}[t]
  \begin{minipage}[t]{0.49\textwidth}
      Negative Algorithmic Variables\\
      $[[α̂⁻]]$, $[[β̂⁻]]$, $[[γ̂⁻]]$, \dots\\
  \end{minipage}%
  \begin{minipage}[t]{0.49\textwidth}
      Positive Algorithmic Variables\\
      $[[α̂⁺]]$, $[[β̂⁺]]$, $[[γ̂⁺]]$, \dots\\
  \end{minipage}

@@

\paragraph*{Auxiliary Functions}
\begin{itemize}
  \item
    We define $[[dom(SC)]]$---the domain of constraint set $[[SC]]$---as a set of
    algorithmic variables that it restricts. Similarly, we define $[[dom(Θ)]]$---the
    domain of instantiation context $[[Θ]]$---as a set of algorithmic variables that
    $[[Θ]]$ associates with their contexts.  
  \item We write $[[Θ(α̂±)]]$ to denote the
    declarative context associated with $[[α̂±]]$ in $[[Θ]]$. 
  \item $[[uv uN]]$ and $[[uv uP]]$ denote the set of free algorithmic variables in $[[uN]]$ and
    $[[uP]]$ respectively.
  \item We write $[[Γ ⊢ Θ]]$ to denote that each
    declarative context associated with an algorithmic variable in $[[Θ]]$ is 
    a subcontext (subset) of $[[Γ]]$.
\end{itemize}

@@

    % Define nodes
    \node[xshift=-1cm] (1) {Negative Subtyping\\$[[Γ ; Θ ⊨ uN ≤ iM ⫤ SC]]$\\(\cref{fig:alg-subtyping})};
    \node[below of=1] (3) {Positive Subtyping\\$[[Γ ; Θ ⊨ uP ≥ iQ ⫤ SC]]$\\(\cref{fig:alg-subtyping})};
    \node[left=1.7cm of 3] (2) {Constraint Merge\\$[[Θ ⊢ SC1 & SC2 = SC3]]$\\(\cref{sec:constraint-merge})};
    \node[right=1.5cm of 3] (5) {Unification\\ $[[Γ ; Θ ⊨ uN ≈u iM ⫤ UC]]$\\ $[[Γ ; Θ ⊨ uP ≈u iQ ⫤ UC]]$\\(\cref{sec:unification})};
    \node[below of=3] (4) {Upgrade\\$[[upgrade Γ ⊢ iP to Δ = iQ]]$\\(\cref{sec:lub})};
    \node[below of=2] (6) {Least Upper Bound\\$[[Γ ⊨ iP1 ∨ iP2 = iQ]]$\\(\cref{sec:lub})};
    \node[below of=6,xshift=.4cm] (7) {Anti-Unification\\$[[Γ ⊨ iP1 ≈au iP2 ⫤ ( Ξ , uQ , aus1 , aus2 )]]$\\$[[Γ ⊨ iN1 ≈au iN2 ⫤ ( Ξ , uM , aus1 , aus2 )]]$\\(\cref{sec:antiunification})};
    \node[below of=5] (8) {Unif. Constraint Merge\\$[[Θ ⊢ UC1 & UC2 = UC3]]$\\(\cref{sec:constraint-merge})};

    % Define edges
    \draw[->] (1) to (2);
    \draw[->] (1) to (3);
    \draw[->] (1) to node[above, draw=none]{$\ottkw{nf}$} (5);
    \draw[->] (2) to (3);
    \draw[->] (2) to (6);
    \draw[->] (3) to (4);
    \draw[->] (3) to node[above, draw=none]{$\ottkw{nf}$} (5);
    \draw[->] (4) to (6);
    \draw[->] (5) to (8);
    \draw[->] (6) to node[left, draw=none]{$\ottkw{nf}$} ($(7.north) + (-.4cm, 0)$);
  \end{tikzpicture}  
  \caption{Dependency graph of the subtyping algorithm}
  \label{fig:alg-subtyping-graph}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \begin{tikzpicture}
    [>={Stealth[scale=2]},node distance=2.1cm,every node/.style={draw,rectangle},every text node part/.style={align=center}]
    % Define nodes
    \node[] (1) {Positive Inference\\$[[Γ; Φ ⊨ v : iP]]$};
    \node[right=1.1cm of 1] (2) {Negative Inference\\$[[Γ; Φ ⊨ c : iN]]$};
    \node[right=0.8cm of 2] (3) {Application Inference\\$[[Γ ; Φ ; Θ1 ⊨ uN ● args ⇒> uM ⫤ Θ2 ; SC]]$};
    \node[below=0.6cm of 2, xshift=+0.4cm] (7) {Minimal Instantiation\\$[[Γ ⊢ uP SC minby uσ]]$\\(\cref{sec:constraint-singularity})};
    \node[below=0.5cm of 7] (8) {Constraint Singularity\\$[[SC singular with uσ]]$\\(\cref{sec:constraint-singularity})};
    \node[right=0.2cm of 7] (4) {Constraint Merge\\$[[Θ ⊢ SC1 & SC2 = SC3]]$\\(\cref{sec:constraint-merge})};
    \node[left=0.3cm of 7] (6) {Negative Subtyping\\$[[Γ ; Θ ⊨ uN1 ≤ iN2 ⫤ SC]]$\\(\cref{sec:subtyping-algorithm})};
    \node[below=0.9cm of 6, xshift=+.3cm] (5) {Positive Subtyping\\$[[Γ ; Θ ⊨ uP1 ≥ iP2 ⫤ SC]]$\\(\cref{sec:subtyping-algorithm})};
    \draw[->] ([yshift=-.2cm]2.west) to ([yshift=-.2cm]1.east);
    \draw[->] ([yshift=+.2cm]1.east) to ([yshift=+.2cm]2.west);
    \draw[->, bend right=20] (3) to (1);
    \draw[->] (2) to (3);
    \draw[->] (2) to ([xshift=+.2cm]4.north west);
    \draw[->] ([xshift=+.4cm]2.south) to (7);
    \draw[->] (3) to (4);
    \draw[->] (7) to (8);
    \draw[->] (1.south west) |- (5);
    \draw[->] ([xshift=+1.2cm]3.south) |- (5.south east);
    \draw[->] (2) to (6);
  \end{tikzpicture}  
  \caption{Dependency graph of the typing algorithm}
  \label{fig:alg-typing-graph}
\end{figure}

@@

\begin{figure}[t]
  \begin{minipage}{0.43\textwidth}
    `$[[SC singular with uσ]]$' means:
    \begin{itemize}[leftmargin=*]
      \item[$+$] for any \emph{positive} constraint entry $[[scE ∊ SC]]$ restricting 
        a variable $[[β̂⁺]]$, there exists $[[iP]]$ such that $[[scE singular with iP]]$
        (as defined in \cref{fig:constraint-entry-singularity}),
        and $[[ [uσ]β̂⁺ = iP ]]$; and
      \item[$-$] the symmetric property holds for all \emph{negative} $[[scE ∊ SC]]$; and
      \item[$\notin$] for any $[[α̂± ∉ dom(SC)]]$, $[[ [uσ]α̂± = α̂± ]]$.
    \end{itemize}
    \caption{Singular Constraint}
    \label{fig:constraint-singularity}
  \end{minipage}
  \begin{minipage}{0.57\textwidth}
    \ottdefnSINGLabeled
    \caption{Singular Constraint Entry}
    \label{fig:constraint-entry-singularity}
  \end{minipage}
\end{figure}

### 2024-07-31 paper/tex/05-proof.tex
WIP: fix references, add appendix
prettify + minor edits

\footnotetext[1]{The presented properties hold, 
            but the actual inductive proof requires strengthening 
            of the statement and the corresponding theorem is more involved. 
            See the appendix (\cref{sec:appendix}) for details.}

@@

\begin{theorem*}[Completeness of Typing]
    \label{thm:completeness-typing}
    Suppose that $[[Γ ⊢ Φ]]$. Then\footnotemark[1]
    \begin{itemize}
        \item [$+$] $[[Γ; Φ ⊢ v : iP]]$ implies $[[Γ; Φ ⊨ v : nf(iP)]]$,
        \item [$-$] $[[Γ; Φ ⊢ c : iN]]$ implies $[[Γ; Φ ⊨ c : nf(iN)]]$,
        \item [$\bullet$] If $[[Γ; Φ ⊢ [uσ]uN ● args ⇒> iM]]$
            where 
            \begin{enumerate*}
                \item $[[Γ ⊢ Θ]]$, 
                \item $[[Γ ⊢ iM]]$,
                \item $[[Γ; dom(Θ) ⊢ uN]]$ (free from \emph{negative} algorithmic variables), and
                \item $[[Θ ⊢ uσ : uv(uN)]]$,
            \end{enumerate*}
            then there exist $[[uM0]]$, $[[Θ0]]$, and $[[SC0]]$ such that
            \begin{enumerate}
                \item $[[ Γ; Φ; Θ ⊨ uN ● args ⇒> uM0 ⫤ Θ0; SC0 ]]$ and
                \item \label{point:mostGeneral} for any other $[[uσ]]$ and $[[iM]]$ 
                (where $[[Θ ⊢ uσ : uv(uN)]]$ and $[[Γ ⊢ iM]]$)
                    such that $[[Γ; Φ ⊢ [uσ]uN ● args ⇒> iM]]$, 
                    there exists $[[uσ']]$ such that 
                    \begin{enumerate*}
                        \item $[[Θ0 ⊢ uσ' : uv uN ∪ uv uM0]]$
                            and $[[Θ0 ⊢ uσ' : SC0]]$,
                        \item $[[Θ ⊢ uσ' ≈ uσ : uv uN]]$, and 
                        \item $[[Γ ⊢ [uσ']uM0 ≈ iM]]$.
                    \end{enumerate*}
            \end{enumerate}
    \end{itemize}
\end{theorem*}

@@

% \begin{lemma*}[Completeness of Unification]
%     \label{lemma:unification-completeness}
%     \hfill
%     \begin{itemize}
%         \item [$+$] For normalized $[[uP]]$ and $[[iQ]]$ such that
%         $[[Γ ; dom(Θ) ⊢ uP]]$ and $[[Γ ⊢ iQ]]$, 
%         suppose that there exists $[[Θ ⊢ uσ : uv(uP)]]$ such that $[[ [uσ]uP = iQ ]]$,
%         then $[[Γ ; Θ ⊨ uP ≈u iQ ⫤ UC]]$ for some $[[UC]]$.

%         \item [$-$] For normalized $[[uN]]$ and $[[iM]]$ such that
%         $[[Γ ; dom(Θ) ⊢  uN]]$ and $[[Γ ⊢ iM]]$,
%         suppose that there exists $[[Θ ⊢ uσ : uv(uN)]]$ such that $[[ [uσ]uN = iM ]]$,
%         then $[[Γ ; Θ ⊨ uN ≈u iM ⫤ UC]]$ for some $[[UC]]$.
%    \end{itemize}
% \end{lemma*}

@@

\begin{lemma*}[Completeness of Positive Subtyping]
    Suppose that $[[Γ ⊢ Θ]]$, $[[Γ ⊢ iQ]]$ and $[[Γ ; dom(Θ) ⊢  uP]]$.
    Then if there exists $[[uσ]]$ such that $[[Θ ⊢ uσ : uv(uP)]]$ and $[[ Γ ⊢ [uσ]uP ≥ iQ ]]$,
    then the subtyping algorithm succeeds: $[[Γ; Θ ⊨ uP ≥ iQ ⫤ SC]]$.
\end{lemma*}

@@

\begin{lemma*}[Completeness of Negative Subtyping]
    Suppose that $[[Γ ⊢ Θ]]$ and $[[Γ ⊢ iM]]$ and $[[Γ ; dom(Θ) ⊢ uN]]$
    and $[[uN]]$ does not contain negative unification variables ($[[α̂⁻]] \notin [[uv uN]]$).
    Then for any $[[Θ ⊢ uσ : uv(uN)]]$ such that $[[Γ ⊢ [uσ]uN ≤ iM]]$,
    the subtyping algorithm succeeds: $[[Γ ; Θ ⊨ uN ≤ iM ⫤ SC]]$.
\end{lemma*}

>>>>

\footnotetext[1]{The presented properties hold, 
            but the actual inductive proof requires strengthening 
            of the statement and the corresponding theorem is more involved. 
            See the appendix (\cref{sec:alg-typing-statements}) for details.}

@@

\begin{theorem*}[Completeness of Typing]
    \label{thm:completeness-typing}
    Suppose that $[[Γ ⊢ Φ]]$. Then\footnotemark[1]
    \begin{itemize}
        \item [$+$] $[[Γ; Φ ⊢ v : iP]]$ implies $[[Γ; Φ ⊨ v : nf(iP)]]$,
        \item [$-$] $[[Γ; Φ ⊢ c : iN]]$ implies $[[Γ; Φ ⊨ c : nf(iN)]]$,
        \item [$\bullet$] If $[[Γ; Φ ⊢ [uσ]uN ● args ⇒> iM]]$
            where 
            \begin{enumerate*}
                \item $[[Γ ⊢ Θ]]$, 
                \item $[[Γ ⊢ iM]]$,
                \item $[[Γ; dom(Θ) ⊢ uN]]$ (free from \emph{negative} algorithmic variables), and
                \item $[[Θ ⊢ uσ : uv uN]]$,
            \end{enumerate*}
            then there exist $[[uM0]]$, $[[Θ0]]$, and $[[SC0]]$ such that
            \begin{enumerate}
                \item $[[ Γ; Φ; Θ ⊨ uN ● args ⇒> uM0 ⫤ Θ0; SC0 ]]$ and
                \item \label{point:mostGeneral} for any other $[[uσ]]$ and $[[iM]]$ 
                (where $[[Θ ⊢ uσ : uv uN]]$ and $[[Γ ⊢ iM]]$)
                    such that $[[Γ; Φ ⊢ [uσ]uN ● args ⇒> iM]]$, 
                    there exists $[[uσ']]$ such that 
                    \begin{enumerate*}
                        \item $[[Θ0 ⊢ uσ' : uv uN ∪ uv uM0]]$
                            and $[[Θ0 ⊢ uσ' : SC0]]$,
                        \item $[[Θ ⊢ uσ' ≈ uσ : uv uN]]$, and 
                        \item $[[Γ ⊢ [uσ']uM0 ≈ iM]]$.
                    \end{enumerate*}
            \end{enumerate}
    \end{itemize}
\end{theorem*}

@@

% \begin{lemma*}[Completeness of Unification]
%     \label{lemma:unification-completeness}
%     \hfill
%     \begin{itemize}
%         \item [$+$] For normalized $[[uP]]$ and $[[iQ]]$ such that
%         $[[Γ ; dom(Θ) ⊢ uP]]$ and $[[Γ ⊢ iQ]]$, 
%         suppose that there exists $[[Θ ⊢ uσ : uv uP]]$ such that $[[ [uσ]uP = iQ ]]$,
%         then $[[Γ ; Θ ⊨ uP ≈u iQ ⫤ UC]]$ for some $[[UC]]$.

%         \item [$-$] For normalized $[[uN]]$ and $[[iM]]$ such that
%         $[[Γ ; dom(Θ) ⊢  uN]]$ and $[[Γ ⊢ iM]]$,
%         suppose that there exists $[[Θ ⊢ uσ : uv uN]]$ such that $[[ [uσ]uN = iM ]]$,
%         then $[[Γ ; Θ ⊨ uN ≈u iM ⫤ UC]]$ for some $[[UC]]$.
%    \end{itemize}
% \end{lemma*}

@@

\begin{lemma*}[Completeness of Positive Subtyping]
    Suppose that $[[Γ ⊢ Θ]]$, $[[Γ ⊢ iQ]]$ and $[[Γ ; dom(Θ) ⊢  uP]]$.
    Then if there exists $[[uσ]]$ such that $[[Θ ⊢ uσ : uv uP]]$ and $[[ Γ ⊢ [uσ]uP ≥ iQ ]]$,
    then the subtyping algorithm succeeds: $[[Γ; Θ ⊨ uP ≥ iQ ⫤ SC]]$.
\end{lemma*}

@@

\begin{lemma*}[Completeness of Negative Subtyping]
    Suppose that $[[Γ ⊢ Θ]]$ and $[[Γ ⊢ iM]]$ and $[[Γ ; dom(Θ) ⊢ uN]]$
    and $[[uN]]$ does not contain negative unification variables ($[[α̂⁻]] \notin [[uv uN]]$).
    Then for any $[[Θ ⊢ uσ : uv uN]]$ such that $[[Γ ⊢ [uσ]uN ≤ iM]]$,
    the subtyping algorithm succeeds: $[[Γ ; Θ ⊨ uN ≤ iM ⫤ SC]]$.
\end{lemma*}
